Harnessing the cloud to understand light: A whitepaper detailing the \MaxwellFDS core solver

### 2013-04-16 thesis/appendix2.tex
Added bibliography and fixed citations.

Our method is now employed to mimic the effect of a sub-diffraction lens.
Since such a lens can be created using a negative-index material \cite{pendry}
    this mimic can be viewed as an imitation of a negative-index material,
    in that the following device recreates the sub-diffraction target-field 
    at the output plane (dotted line)
    when illuminated by the same target field at the input of the device.
In other words,
    this device is an image-specific sub-diffraction imager,
    which is another way of saying that it is a single-mode imager.
\myfig{mimic/m2}{Sub-diffraction lens mimic.
                The target field has a full-width half-maximum of 0.14 $\lambda$.
                Error: 28.6\%,
                device footprint: $60 \times 120$ grid points (1.43 $\lambda$ thick),
                wavelength: 42 grid points.}

>>>>

Our method is now employed to mimic the effect of a sub-diffraction lens.
Since such a lens can be created using a negative-index material \cite{Pendry00}
    this mimic can be viewed as an imitation of a negative-index material,
    in that the following device recreates the sub-diffraction target-field 
    at the output plane (dotted line)
    when illuminated by the same target field at the input of the device.
In other words,
    this device is an image-specific sub-diffraction imager,
    which is another way of saying that it is a single-mode imager.
\myfig{mimic/m2}{Sub-diffraction lens mimic.
                The target field has a full-width half-maximum of 0.14 $\lambda$.
                Error: 28.6\%,
                device footprint: $60 \times 120$ grid points (1.43 $\lambda$ thick),
                wavelength: 42 grid points.}

### 2013-04-16 thesis/appendix3.tex
Added bibliography and fixed citations.

The optimization paradigm utilizes 
    the alternating directions method of multipliers\cite{ADMM} (ADMM) optimization technique, 
    which casts \eq{rigorous problem statement} in terms of the following augmented Lagrangians, 
    \E{}{\Lag(x, z, y) = \sum_i^N f_i(x_i) 
            + \frac{\rho}{2} \norm{A_i(z) x_i - b_i(z)}^2 
            +\real\left[y_i^\cT (A_i(z)x_i-b_i(z))\right] + g(z),}
    where $\rho$ is a constant scalar and 
    $y_i$ are dual variables. If we introduce $u_i = y_i / \rho$, then 
    \E{}{\Lag(x,z,u) = \sum_i^N f_i(x_i)
            + \frac{\rho}{2} \norm{A_i(z) x_i - b_i(z) + u_i}^2 
            - \frac{\rho}{2} \norm{u_i}^2 + g(z).}

>>>>

The optimization paradigm utilizes 
    the alternating directions method of multipliers\cite{Boyd11} (ADMM) optimization technique, 
    which casts \eq{rigorous problem statement} in terms of the following augmented Lagrangians, 
    \E{}{\Lag(x, z, y) = \sum_i^N f_i(x_i) 
            + \frac{\rho}{2} \norm{A_i(z) x_i - b_i(z)}^2 
            +\real\left[y_i^\cT (A_i(z)x_i-b_i(z))\right] + g(z),}
    where $\rho$ is a constant scalar and 
    $y_i$ are dual variables. If we introduce $u_i = y_i / \rho$, then 
    \E{}{\Lag(x,z,u) = \sum_i^N f_i(x_i)
            + \frac{\rho}{2} \norm{A_i(z) x_i - b_i(z) + u_i}^2 
            - \frac{\rho}{2} \norm{u_i}^2 + g(z).}

### 2013-04-16 thesis/chapter1.tex
Added bibliography and fixed citations.

\section{Results}
We now solve \eq{p1:problem} to design nanophotonic resonators in 1D.
We use the magnetic field formulation of the electromagnetic equation
    in the following examples;
    analogous results for the original $E$-field formulation (\eq{p1:wave})
    are expected.

@@

\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{p1/leastsquares}
\caption{Design of a one-dimensional structure using the direct design method.
    The target field is a sinusoid within a Gaussian envelope. 
    The computed dielectric structure (green area) supports 
        a field (red circles) that exactly matches the target field (blue line). 
    The entire design process is extremely fast and takes less than 
        $1$ second to complete on a generic desktop computer~\cite{mycomp}. 
    Unfortunately, the periodic singularities in the dielectric structure 
        mean that such a structure is unrealizable in practice.}
\label{p1:direct}\end{figure}

@@

\section{Results}
We chose to constrain the values of $z$ ($\epsilon$) 
    around a constant value of $z_0, \epsilon_0 = 10$ and 
    solved \eq{reg:problem} for $\eta=10^{-8}$, $10^{-6}$, and $10^{-4}$;
    the results of which are shown in fig.~\ref{regls pic}.

>>>>

\section{Results}
We now solve \eq{p1:problem} to design nanophotonic resonators in 1D\cite{Lu10}.
We use the magnetic field formulation of the electromagnetic equation
    in the following examples;
    analogous results for the original $E$-field formulation (\eq{p1:wave})
    are expected.

@@

\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{p1/leastsquares}
\caption{Design of a one-dimensional structure using the direct design method.
    The target field is a sinusoid within a Gaussian envelope. 
    The computed dielectric structure (green area) supports 
        a field (red circles) that exactly matches the target field (blue line). 
    The entire design process is extremely fast and takes less than 
        $1$ second to complete on a generic desktop computer.
    Unfortunately, the periodic singularities in the dielectric structure 
        mean that such a structure is unrealizable in practice.}
\label{p1:direct}\end{figure}

@@

\section{Results}
We chose to constrain the values of $z$ ($\epsilon$) 
    around a constant value of $z_0, \epsilon_0 = 10$ and 
    solved \eq{reg:problem} for $\eta=10^{-8}$, $10^{-6}$, and $10^{-4}$;
    the results of which are shown in fig.~\ref{regls pic}\cite{Lu10}.

### 2013-04-16 thesis/chapter2.tex
Added bibliography and fixed citations.

\section{Results}
\subsection{1D}
Fig.~\ref{comp pic} shows that the iterative algorithm, after $400$ iterations and with the correct choice of regularization parameters $\eta_0$ and $\eta_1$, results in a well-behaved structure that is able to closely reproduce the modified target field.

@@

\subsection{2D}
The iterative design method can also be extended to two dimensions.
We demonstrate this using an S-shaped target field 
    which is non-trivial to reproduce. 
The design result is shown in fig.~\ref{S pic}. 
    The resulting dielectric structure is continuous, unbounded and 
    contains very few singularities (white dots), 
    but the final target and actual fields match up well. 
Also, the computational cost remains quite reasonable; the $50$ iterations needed required only $5$ minutes of computation time. 
\begin{figure}\centering
\includegraphics[width=\textwidth]{p1/S}
\caption{Iterative design of an ``S'' resonator. 
The design was initialized by specifying an initial dielectric structure ($\epsilon=1$ everywhere) and a resonant field in the shape of an ``S''. 
The final dielectric structure was produced after $50$ iterations which took $90$ seconds to complete in total. The grid size was $80\times 120$. The final dielectric structure is quite unintuive, and yet reproduces the target field surprisingly well. This example demonstrates the versatility of the iterative design method in producing designs, from very simple specifications, which otherwise could be attained only with considerable difficulty.}
\label{S pic}
\end{figure}

@@

\section{Implementation} 
In this algorithm, \eq{bounded problem} is no longer linear in $z$
    but is still convex\cite{BV04}.
For this reason, the \emph{CVX} package\cite{CVX}, 
    a Matlab-based modeling system for convex optimization, 
    is now used to solve \eq{bounded problem} for $z$.

\section{Results}
\subsection{1D}
Once again, we attempt the design of a one-dimensional resonator
    and find thata nearly binary-valued dielectric structure is obtained,
    as seen in fig.~\ref{bounded comp pic}.
Note that the the directly discreteness of $z$ was not enforced (since that would make the problem non-convex); 
    however, a discrete, binary-valued structure arose fortuitously. 
Critically, this dielectric structure accurately produces the final target field.

@@

We now use the complementary optimization method to design resonators with discrete, binary $\epsilon$ in two dimensions.

Fig.~\ref{circle pic} shows the design of a circular grating resonator. 
The dielectric structure emerged from a very simple choice of initial structure, 
    namely a constant $\epsilon=12.25$ everywhere. 
The range of $\epsilon$ was limited to be from $1$ to $12.25$.
Additionally, the components of $\epsilon$ outside a specified circle 
    were held at a constant $\epsilon=12.25$ 
    for the duration of the design process. 
The entire algorithm was run for $40$ iterations and took $7$ minutes.
Interestingly, the central bowtie-like structure has emerged 
    from previous genetic optimization methods as well\cite{Lip08}.

@@

Therefore, to make our problem more tractable, we formulate a 2.5-dimensional approximation of the electromagnetic fields of a planar three-dimensional nanophotonic device. As shown in Fig.~\ref{approx}a, this involves treating a planar three-dimensional nanophotonic device as a truncated holey fiber with identical dielectric structure. We take advantage of the planar nature of most nanophotonic devices in this way to produce a tractable, computationally-fast method. The $E$-field inside such a holey fiber is expressed as
\begin{equation}
E = E(x,y)e^{-i\beta z},
\end{equation}
where $\beta$ is the wave-vector along the fiber axis. Solving for Eq.~\ref{wave} now requires solving for a much smaller ($\sim 10^5 \times 10^5$) matrix, which can be accomplished using standard linear algebra packages. This simulation technique is thus very similar to a two-dimensional finite-difference frequency-domain solve.

@@

In this approximation, converting from a 2.5-dimensional structure to a full three-dimensional structure only requires the correct choice of slab thickness, $t$, since the in-plane values of $\epsilon$ remain the same. To estimate $t$ for the full three-dimensional device, we treat the resonant mode as a guided mode in a slab waveguide surrounded by a cladding of $n=1$. The expression for $t$ is then the thickness of the slab for the lowest-order TE mode of a slab waveguide with effective refractive index $n_\text{eff}$\cite{inan}:
\begin{align}
t &= \frac{2}{\beta}\tan^{-1}\frac{\alpha}{\beta},\label{t} \quad\text{where} \\
\alpha &= \sqrt{k_x^2 - \left(\frac{\omega}{c}\right)^2}, \quad\text{and} \\
k_x &= \sqrt{\left(\frac{n_\text{eff}\omega}{c}\right)^2 - \beta^2}.
\end{align}
Here, $\alpha$ is the wave-vector which determines the evanescent decay of the slab waveguide mode into air, while $k_x$ is an approximated in-plane k-vector. To determine $n_\text{eff}$, the effective refractive index, we use the following approximation,
\begin{equation}
n_\text{eff} = \sqrt{\frac{\|\epsilon E^2\|}{\|E^2\|}}.
\end{equation}
% In the above formulation and for the remainder of the manuscript, the norm ($\|\cdot\|$) refers to the 2-norm over the entire grid and is equivalent to the spatial integral $(\int | \cdot |^2 dr)^{1/2}$.

@@

Using \eq{iterative problem}, along with our 2.5-dimensional approximation, the iterative design of a planar three-dimensional nanophotonic device is performed.

>>>>

\section{Results}
\subsection{1D}
Fig.~\ref{comp pic} shows that the iterative algorithm, after $400$ iterations and with the correct choice of regularization parameters $\eta_0$ and $\eta_1$, results in a well-behaved structure that is able to closely reproduce the modified target field\cite{Lu10}.

@@

\subsection{2D}
The iterative design method can also be extended to two dimensions\cite{Lu10}.
We demonstrate this using an S-shaped target field 
    which is non-trivial to reproduce. 
The design result is shown in fig.~\ref{S pic}. 
    The resulting dielectric structure is continuous, unbounded and 
    contains very few singularities (white dots), 
    but the final target and actual fields match up well. 
Also, the computational cost remains quite reasonable; the $50$ iterations needed required only $5$ minutes of computation time. 
\begin{figure}\centering
\includegraphics[width=\textwidth]{p1/S}
\caption{Iterative design of an ``S'' resonator. 
The design was initialized by specifying an initial dielectric structure ($\epsilon=1$ everywhere) and a resonant field in the shape of an ``S''. 
The final dielectric structure was produced after $50$ iterations which took $90$ seconds to complete in total. The grid size was $80\times 120$. The final dielectric structure is quite unintuive, and yet reproduces the target field surprisingly well. This example demonstrates the versatility of the iterative design method in producing designs, from very simple specifications, which otherwise could be attained only with considerable difficulty.}
\label{S pic}
\end{figure}

@@

\section{Implementation} 
In this algorithm, \eq{bounded problem} is no longer linear in $z$
    but is still convex\cite{Boyd04}.
For this reason, the \emph{CVX} package\cite{Grant09}, 
    a Matlab-based modeling system for convex optimization, 
    is now used to solve \eq{bounded problem} for $z$.

\section{Results}
\subsection{1D}
Once again, we attempt the design of a one-dimensional resonator
    and find that a nearly binary-valued dielectric structure is obtained,
    as seen in fig.~\ref{bounded comp pic}\cite{Lu10}.
Note that the the directly discreteness of $z$ was not enforced (since that would make the problem non-convex); 
    however, a discrete, binary-valued structure arose fortuitously. 
Critically, this dielectric structure accurately produces the final target field.

@@

We now use the complementary optimization method to design resonators with discrete, binary $\epsilon$ in two dimensions\cite{Lu10}.

Fig.~\ref{circle pic} shows the design of a circular grating resonator. 
The dielectric structure emerged from a very simple choice of initial structure, 
    namely a constant $\epsilon=12.25$ everywhere. 
The range of $\epsilon$ was limited to be from $1$ to $12.25$.
Additionally, the components of $\epsilon$ outside a specified circle 
    were held at a constant $\epsilon=12.25$ 
    for the duration of the design process. 
The entire algorithm was run for $40$ iterations and took $7$ minutes.
Interestingly, the central bowtie-like structure has emerged 
    from previous genetic optimization methods as well\cite{Gond08}.

@@

Therefore, to make our problem more tractable, we formulate a 2.5-dimensional approximation of the electromagnetic fields of a planar three-dimensional nanophotonic device\cite{Lu11}. As shown in Fig.~\ref{approx}a, this involves treating a planar three-dimensional nanophotonic device as a truncated holey fiber with identical dielectric structure. We take advantage of the planar nature of most nanophotonic devices in this way to produce a tractable, computationally-fast method. The $E$-field inside such a holey fiber is expressed as
\begin{equation}
E = E(x,y)e^{-i\beta z},
\end{equation}
where $\beta$ is the wave-vector along the fiber axis. Solving for Eq.~\ref{wave} now requires solving for a much smaller ($\sim 10^5 \times 10^5$) matrix, which can be accomplished using standard linear algebra packages. This simulation technique is thus very similar to a two-dimensional finite-difference frequency-domain solver.

@@

In this approximation, converting from a 2.5-dimensional structure to a full three-dimensional structure only requires the correct choice of slab thickness, $t$, since the in-plane values of $\epsilon$ remain the same. To estimate $t$ for the full three-dimensional device, we treat the resonant mode as a guided mode in a slab waveguide surrounded by a cladding of $n=1$. The expression for $t$ is then the thickness of the slab for the lowest-order TE mode of a slab waveguide with effective refractive index $n_\text{eff}$\cite{Inan00}:
\begin{align}
t &= \frac{2}{\beta}\tan^{-1}\frac{\alpha}{\beta},\label{t} \quad\text{where} \\
\alpha &= \sqrt{k_x^2 - \left(\frac{\omega}{c}\right)^2}, \quad\text{and} \\
k_x &= \sqrt{\left(\frac{n_\text{eff}\omega}{c}\right)^2 - \beta^2}.
\end{align}
Here, $\alpha$ is the wave-vector which determines the evanescent decay of the slab waveguide mode into air, while $k_x$ is an approximated in-plane k-vector. To determine $n_\text{eff}$, the effective refractive index, we use the following approximation,
\begin{equation}
n_\text{eff} = \sqrt{\frac{\|\epsilon E^2\|}{\|E^2\|}}.
\end{equation}
% In the above formulation and for the remainder of the manuscript, the norm ($\|\cdot\|$) refers to the 2-norm over the entire grid and is equivalent to the spatial integral $(\int | \cdot |^2 dr)^{1/2}$.

@@

Using \eq{iterative problem}, along with our 2.5-dimensional approximation, the iterative design of a planar three-dimensional nanophotonic device is performed\cite{Lu11}.

### 2013-04-16 thesis/chapter3.tex
Added bibliography and fixed citations.

\begin{figure}[htb]
    \centering
    \includegraphics[width=\textwidth]{p3/intro} 
    \caption{Boundary-value formulation of the design objective.
        The values of $H_z^\text{perfect}$, 
            defined along the dashed box surrounding the design area
            (coupling structure), 
            are shown in orange. 
        The values of $H_z^\text{perfect}$ along the top and bottom edges
            of the dashed box are set to zero.
        In this schematic, the fundamental and second-order waveguide modes
            have been chosen as the input and output modes respectively.}
    \label{fig:intro}
\end{figure}
%\section{Objective-first design of waveguide couplers}
% We now demonstrate the objective-first approach
%     by designing waveguide couplers in two-dimensions.
% As such, we do not analyze effects which are only present in full 
%     three-dimensional systems, such as out-of-plane losses.
% Specifically, we work in the two-dimensional transverse electric mode,
%     choosing $H_z$ as the field variable $x$,
%     and $\epsilon^{-1}$ (the inverse of the permittivity) 
%     as the structure variable $p$.
% This results in the following form of the physics residual,
%     \begin{equation}
%     \|g(x,p)\|^2 = 
%     \|g(H_z, \epsilon^{-1})\|^2 = 
%     \| \nabla \times \epsilon^{-1} \nabla \times H_z - \mu_0 \omega^2 H_z \|^2,
%     \end{equation}
%     where $\omega$ is the angular frequency,
%     and $\mu_0$ is the permeability of free-space.
% 
% In order to produce a method applicable 
%     to the design of any linear nanophotonic device,
%     we note that its performance
%     will be completely characterized by the fields along its boundary,
%     and therefore, 
%     we choose a boundary-value formulation for the design objective 
%     as shown in Fig.~\ref{fig:intro}.
% Namely, we first compute the boundary fields needed to obtain
%     perfect performance, $H_z^\text{perfect}$,
%     and then form the design objective as
%     \begin{equation}
%     f(x) = f(H_z) = \begin{bmatrix}
%         H_z - H_z^\text{perfect} \\
%         \frac{\partial H_z}{\partial n} - 
%             \frac{\partial H_z^\text{perfect}}{\partial n}
%         \end{bmatrix}_\text{boundary}
%         = 0,
%     \end{equation}
%     where $\partial H_z / \partial n$ 
%     denotes the spatial derivative in the direction normal to the boundary.
% 
% \begin{figure}[htb]
%     \centering
%     \includegraphics[width=\textwidth]{p3/intro} 
%     \caption{Boundary-value formulation of the design objective.
%         The values of $H_z^\text{perfect}$, 
%             defined along the dashed box surrounding the design area
%             (coupling structure), 
%             are shown in orange. 
%         The values of $H_z^\text{perfect}$ along the top and bottom edges
%             of the dashed box are set to zero.
%         In this schematic, the fundamental and second-order waveguide modes
%             have been chosen as the input and output modes respectively.}
%     \label{fig:intro}
% \end{figure}
%     
Such a design objective is both extremely simple and widely adaptable 
    to the design of linear nanophotonic devices in general.
On the other hand, such a formulation often prohibits the physics residual 
    from disappearing completely; 
    however, we find that very good device performance is still obtained
    as long as the physics residual is sufficiently small.

@@

Specifically, we present five results which suggest our method
    is indeed able to design arbitrary single-mode, linear nanophotonic devices.
These results comprise of couplers between 
    the following nanophotonic waveguides:
    \begin{enumerate}
    \item coupling between waveguides of different refractive index and width
        (Fig.~\ref{fig:fiber});
    \item coupling between waveguide modes of different order and symmetry
        (Fig.~\ref{fig:mode});
    \item coupling between waveguides that confine light 
        using different principles 
        (index guided vs. distributed Bragg reflection guided), 
        i.e., between a slab waveguide and a photonic crystal fiber
        (Fig.~\ref{fig:aircore})
    \item coupling from a dielectric to a plasmonic metal-insulator-metal 
        waveguide (Fig.~\ref{fig:mim}); and
    \item coupling from a dielectric waveguide to a (plasmonic) metal wire
        (Fig.~\ref{fig:wire}).
    \end{enumerate}
All the designs presented are both highly efficient 
    ($\sim 98\%$ coupling efficiency, in contrast to previous designs
    which achieve only $\sim 70\%$ coupling efficiency\cite{veronis,yang})
    and extremely compact 
    (with footprints of only 1.5-4 square vacuum wavelengths).

>>>>

\begin{figure}[htb]
    \centering
    \includegraphics[width=\textwidth]{p3/intro} 
    \caption{Boundary-value formulation of the design objective.
        The values of $H_z^\text{perfect}$, 
            defined along the dashed box surrounding the design area
            (coupling structure), 
            are shown in orange. 
        The values of $H_z^\text{perfect}$ along the top and bottom edges
            of the dashed box are set to zero.
        In this schematic, the fundamental and second-order waveguide modes
            have been chosen as the input and output modes respectively.}
    \label{fig:intro}
\end{figure}
%\section{Objective-first design of waveguide couplers}
% We now demonstrate the objective-first approach
%     by designing waveguide couplers in two-dimensions.
% As such, we do not analyze effects which are only present in full 
%     three-dimensional systems, such as out-of-plane losses.
% Specifically, we work in the two-dimensional transverse electric mode,
%     choosing $H_z$ as the field variable $x$,
%     and $\epsilon^{-1}$ (the inverse of the permittivity) 
%     as the structure variable $p$.
% This results in the following form of the physics residual,
%     \begin{equation}
%     \|g(x,p)\|^2 = 
%     \|g(H_z, \epsilon^{-1})\|^2 = 
%     \| \nabla \times \epsilon^{-1} \nabla \times H_z - \mu_0 \omega^2 H_z \|^2,
%     \end{equation}
%     where $\omega$ is the angular frequency,
%     and $\mu_0$ is the permeability of free-space.
% 
% In order to produce a method applicable 
%     to the design of any linear nanophotonic device,
%     we note that its performance
%     will be completely characterized by the fields along its boundary,
%     and therefore, 
%     we choose a boundary-value formulation for the design objective 
%     as shown in Fig.~\ref{fig:intro}.
% Namely, we first compute the boundary fields needed to obtain
%     perfect performance, $H_z^\text{perfect}$,
%     and then form the design objective as
%     \begin{equation}
%     f(x) = f(H_z) = \begin{bmatrix}
%         H_z - H_z^\text{perfect} \\
%         \frac{\partial H_z}{\partial n} - 
%             \frac{\partial H_z^\text{perfect}}{\partial n}
%         \end{bmatrix}_\text{boundary}
%         = 0,
%     \end{equation}
%     where $\partial H_z / \partial n$ 
%     denotes the spatial derivative in the direction normal to the boundary.
% 
% \begin{figure}[htb]
%     \centering
%     \includegraphics[width=\textwidth]{p3/intro} 
%     \caption{Boundary-value formulation of the design objective.
%         The values of $H_z^\text{perfect}$, 
%             defined along the dashed box surrounding the design area
%             (coupling structure), 
%             are shown in orange. 
%         The values of $H_z^\text{perfect}$ along the top and bottom edges
%             of the dashed box are set to zero.
%         In this schematic, the fundamental and second-order waveguide modes
%             have been chosen as the input and output modes respectively.}
%     \label{fig:intro}
% \end{figure}
%     
Such a design objective is both extremely simple and widely adaptable 
    to the design of linear nanophotonic devices in general\cite{Miller12}.
On the other hand, such a formulation often prohibits the physics residual 
    from disappearing completely; 
    however, we find that very good device performance is still obtained
    as long as the physics residual is sufficiently small.

@@

Specifically, we present five results which suggest our method
    is indeed able to design arbitrary single-mode, linear nanophotonic devices\cite{Lu12}.
These results comprise of couplers between 
    the following nanophotonic waveguides:
    \begin{enumerate}
    \item coupling between waveguides of different refractive index and width
        (Fig.~\ref{fig:fiber});
    \item coupling between waveguide modes of different order and symmetry
        (Fig.~\ref{fig:mode});
    \item coupling between waveguides that confine light 
        using different principles 
        (index guided vs. distributed Bragg reflection guided), 
        i.e., between a slab waveguide and a photonic crystal fiber
        (Fig.~\ref{fig:aircore})
    \item coupling from a dielectric to a plasmonic metal-insulator-metal 
        waveguide (Fig.~\ref{fig:mim}); and
    \item coupling from a dielectric waveguide to a (plasmonic) metal wire
        (Fig.~\ref{fig:wire}).
    \end{enumerate}
All the designs presented are both highly efficient 
    ($\sim 98\%$ coupling efficiency, in contrast to previous designs
    which achieve only $\sim 70\%$ coupling efficiency\cite{Veronis07,Yang10})
    and extremely compact 
    (with footprints of only 1.5-4 square vacuum wavelengths).

### 2013-04-16 thesis/chapter4.tex
Added bibliography and fixed citations.

    linear nanophotonic device which

@@

    In contrast to typical schemes for optimizing physical structures,
        our formulation actually allows for non-zero physics residuals;
        which can be deduced since $A_i(z)x_i-b_i=0$ is not a hard constraint.
    Instead, this formulation is what also an \emph{objective-first} \cite{ob1_wg}
        formulation in that the \emph{design objective} (explained below)
        is prioritized above satisfying physics.

@@

\section{Implementation}
We employed the alternating directions method of multipliers (ADMM) algorithm 
    \cite{admm}
    in order to solve \eq{problem}.
The ADMM algorithm solves \eq{problem} by iteratively solving for 
    $x_i$, $z$, and a dual variable $u_i$.

Since we are working in three dimensions, solving \eq{problem} for $x_i$ 
    is non-trivial in that it involves millions of variables and
    requires solving for the ill-conditioned $A_i(z)$ matrix.
For this reason, we use a home-built
    finite-difference frequency-domain (FDFD) solver which 
    implements a hardware-accelerated iterative solver\cite{wonseok}
    on Amazon's Elastic Compute Cloud.
Critically, our cloud-based solver allows us to scale to solve problems
    with arbitrarily-large number of modes,
    with no significant penalty in runtime.

@@

Lastly, in order to arrive at fully discrete, manufacturable structures,
    we convert $z$ to a boundary parameterization\cite{levelset}
    and tune our structure using a steepest-descent method.

@@

\section{Results}
We demonstrate the effectiveness of our design method 
    by producing designs for a variety of nanophotonic devices.

@@

\subsubsection{Spatial mode splitter}
We demonstrate what is, to our knowledge, 
    the first design for a three-dimensional
    nanophotonic spatial mode splitter 
    (previous designs were restricted to two dimensions \cite{2dsplitter}).
Such a device is the key enabler for multi-mode on-chip optical circuits,
    and we show here that they can be designed to be highly efficient
    while utilizing a very small device footprint ($2.8\times2.8$ microns). 
The performance specification is shown in \fig{3Db_spl_modal},
    and the final results is shown in \fig{spl_modal}.

@@

\subsection{Fiber couplers}
The capabilities of our method are further demonstrated
    in the design of nanophotonic fiber couplers,
    which couple light from an optical fiber at normal incidence
    into an in-plane waveguide\cite{baets}.

>>>>

    linear nanophotonic devices which

@@

    In contrast to typical schemes for optimizing physical structures,
        our formulation actually allows for non-zero physics residuals;
        which can be deduced since $A_i(z)x_i-b_i=0$ is not a hard constraint.
    Instead, this formulation is what also an \emph{objective-first} \cite{Lu12}
        formulation in that the \emph{design objective} (explained below)
        is prioritized above satisfying physics.

@@

\section{Implementation}
We employed the alternating directions method of multipliers (ADMM) algorithm 
    \cite{Boyd11}
    in order to solve \eq{problem}.
The ADMM algorithm solves \eq{problem} by iteratively solving for 
    $x_i$, $z$, and a dual variable $u_i$.

Since we are working in three dimensions, solving \eq{problem} for $x_i$ 
    is non-trivial in that it involves millions of variables and
    requires solving for the ill-conditioned $A_i(z)$ matrix.
For this reason, we use a home-built
    finite-difference frequency-domain (FDFD) solver which 
    implements a hardware-accelerated iterative solver\cite{Shin12}
    on Amazon's Elastic Compute Cloud.
Critically, our cloud-based solver allows us to scale to solve problems
    with arbitrarily-large number of modes,
    with no significant penalty in runtime.

@@

Lastly, in order to arrive at fully discrete, manufacturable structures,
    we convert $z$ to a boundary parameterization\cite{Osher02}
    and tune our structure using a steepest-descent method.

@@

\section{Results}
We demonstrate the effectiveness of our design method 
    by producing designs for a variety of nanophotonic devices\cite{Lu13}.

@@

\subsubsection{Spatial mode splitter}
We demonstrate what is, to our knowledge, 
    the first design for a three-dimensional
    nanophotonic spatial mode splitter 
    (previous designs were restricted to two dimensions \cite{Jiao05}).
Such a device is the key enabler for multi-mode on-chip optical circuits,
    and we show here that they can be designed to be highly efficient
    while utilizing a very small device footprint ($2.8\times2.8$ microns). 
The performance specification is shown in \fig{3Db_spl_modal},
    and the final results is shown in \fig{spl_modal}.

@@

\subsection{Fiber couplers}
The capabilities of our method are further demonstrated
    in the design of nanophotonic fiber couplers,
    which couple light from an optical fiber at normal incidence
    into an in-plane waveguide\cite{Laere07}.
